Convective penetration: It exists and we found it

### 2021-07-27 manuscript/ms.tex
some small edits

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Modern numerical experiments often examine the importance of the ``stiffness'' $\mS$ of a radiative-convective interface.
$\mS$ compares the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[dating back to e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
A link between $\mS$ and the processes of entrainment and overshoot has seemingly emerged, but a mechanism for penetration remains elusive.

@@

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

\subsection{Convective penetration \& this study's findings}

@@

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can better constrain this theory in Sec.~\ref{sec:discussion}.

@@

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{parameter_space.pdf}
\caption{
Each point corresponds to a simulations conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty markers are simulations with stress-free boundary conditions while filled-in markers are simulations with no-slip boundary conditions. 
We additionally conduct simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
The two ``landmark'' simulations are denoted by boxes.
The landmark Case I simulation has $\mR = 400$ and $\mP_D = 4$.
The landmark Case II simulation has $\mR = 800$ and $\mP_L = 4$.
Both landmark simulations have $\mS = 10^3$ and no-slip boundary conditions.
\label{fig:parameter_space}
}
\end{figure}

@@

\subsection{Dynamics}
In Fig.~\ref{fig:lessturb_dynamics_panels} we display snapshots of the temperature anomalies in the two ``landmark'' simulations denoted by boxes in Fig.~\ref{fig:parameter_space}.
We display the temperature anomaly in the top panel of the Case I simulation with $\mR = 400$, $\mP_D = 4$, and $\mS = 10^3$; this simulation is included in all three of our parameter space sweeps and represents the point where our ($\mR, \mP, \mS$) cuts converge  in Fig.~\ref{fig:parameter_space}.
We display the temperature anomaly in the bottom panel of the Case II simulation with $\mR = 800$, $\mP_L = 4$, and $\mS = 10^3$.
The bulk reynolds number in the convection zones of these simulations are (top) $\sim 250$ and (bottom) $\sim 350$.
Thus, these simulations are less turbulent than the simulation in Fig.~\ref{fig:vertical_dynamics_panels} (bulk Re $\sim$ 5000).
Aside from the degree of turbulence, the dynamics are very similar in Figs.~\ref{fig:vertical_dynamics_panels} \& \ref{fig:lessturb_dynamics_panels}.
In particular, we observe that hot plumes in the CZ turn into cold plumes in the PZ (as they cross the dashed horizontal lines), and hot downflows in the PZ turn into cold downflows in the CZ.
Convective plumes extend through the penetrative region and impact the stable radiative zone (above the solid horizontal line).
The interface with the radiative zone is stiff, and so convective motions excite waves at a shallow angle above the radiative-convective boundary.
We note that the Case II simulation has an additional temperature inversion at the base of the simulation.
Case II simulations have a linearly increasing conductivity $k$ in the convection zone, so there is formally a small penetrative region where $\justgrad \approx \gradad > \gradrad$ at the base of the domain below the internal heating layer.

@@

\begin{figure*}[t]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
(Left panel) Penetration heights are shown vs.~$\mS$.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{parameters_vs_re.pdf}
\caption{
(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations (see vertical cut in Fig.~\ref{fig:parameter_space}).
We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
(Upper middle panel) $f$ also increases with $\mR$.
(Upper right panel) $\xi$ does not change appreciably with $\mR$ for turbulent simulations with $\mR \geq 200$.
(Lower left panel) There is a strong correlation between $\delta_{0.5}$ and $f$, agreeing with our theoretical model of Eqn.~\ref{eqn:discontinuous_prediction}.
(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
Boxed data points show the location of landmark simulation from Fig.~\ref{fig:parameter_space}.
\label{fig:parameters_vs_re}
}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{mesa_profiles.pdf}
\caption{
(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a MESA solar model with a penetration zone.
(bottom) Sound speed differences between the model shown in the top panel and a standard (std) model run at identical parameters but without a PZ.
The addition of a PZ creates an acoustic glitch, raising the sound speed by $\mathcal{O}$(2\%) below the convection zone.
\label{fig:mesa_profiles}
}
\end{figure}

@@

In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
\begin{equation}
\int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
\label{eqn:mesa_integral_constraint}
\end{equation}
where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$, $r$ is the radial coordinate, and we write the RHS as a volume integral.
We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
\begin{equation}
\int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
\label{eqn:sphere_xi_defn}
\end{equation}
where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
\begin{equation}
-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}} = (1 - f),
\label{eqn:mesa_eqn}
\end{equation}

We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and evolved a $1 M_\odot$ model to an age of 4.56 Gyr with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to qualitatively understand how our penetration parameterization modifies a stellar model.
In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from the model which includes convective penetration.
Note that $\justgrad$ (green) remains close to $\gradad$ (purple) below the Schwarzschild convective boundary ($\gradad = \gradrad$) in a penetration zone.
After some depth $\justgrad \rightarrow \gradrad$ (orange) in the star's interior.
We additionally evolved a standard 1 $M_\odot$ MESA model to a 4.56 Gyr age without the inclusion of a PZ.
We compare the sound speed $c$ profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).

@@

\section{Discussion}
\label{sec:discussion}
In this work, we presented dynamical simulations of convective penetration, in which convection flattens $\justgrad \rightarrow \gradad$ beyond the Schwarzschild boundary.
To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
We briefly examined what the impliciations of this theory could be for a simple stellatellarr model.

@@

Furthermore, it is important to note that stellar opacities, and thus stellar conductivities, are functions of thermodynamic variables rather than radial location.
As a result, the formation of a penetration zone will in turn affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
In other words, the combined effects of penetration and entrainment should be considered.
Future studies should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.

An additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$ and $\xi$.
Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
Future work should aim to understand whether $f$ and/or $\xi$ depend strongly on $\Pran$ in the turbulent regime.

@@

Our work here assumes a uniform composition through the convective and radiative region.
Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here (as in Fig.~\ref{fig:time_evolution}).

In summary, we have unified \citet{roxburgh1989}'s integral constraint with \citet{zahn1991}'s theory of flux-dependent penetration into a parameterized theory of convective penetration.
We tested this theory with simulations and found good agreement between the theory and our simulations.
In future work, we will aim to more robustly implement this theory into MESA and use simulations to test some of the complicating factors we discussed here.

>>>>

Convective overshoot, penetration, and entrainment have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Experiments exhibiting extensive expansion of convection zones via entrainment have a long history \citep[e.g.,][and this process is often confusingly called ``penetration'']{musman1968, deardorff_etal_1969, moore_weiss_1973}.
Modern numerical experiments often examine the importance of the ``stiffness'' $\mS$ of a radiative-convective interface.
$\mS$ compares the relative stability of a radiative zone and an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Some recent studies in simplified Boussinesq setups exhibit stiffness-dependent convection zone expansion via entrainment \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}; others find stiffness-dependent pure overshoot \citep{korre_etal_2019}.
A link between $\mS$ and the processes of entrainment and overshoot has seemingly emerged, but a mechanism for penetration remains elusive.

@@

There are hints in the literature that convective penetration may depend on energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy equation and found that a spatial integral of the flux puts an upper limit on the size of a theoretical penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this idea, and found that penetration lengths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_glatzmaier_2005} may agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of energy fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

$\,$
\subsection{Convective penetration \& this study's findings}

@@

We present these findings as follows.
In Sec.~\ref{sec:central_results}, we present the central finding of this work: penetration zones in nonlinear convective simulations.
In Sec.~\ref{sec:theory}, we describe the equations used and derive a parameterized theory of convective penetration.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the height of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a stellar model in MESA which has convective penetration.
Finally, we discuss pathways for future work in Sec.~\ref{sec:discussion}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{parameter_space.pdf}
\caption{
Each marker corresponds to a simulation conducted in this work in the $\mR-\mP$ parameter space at $\mS = 10^3$. 
Purple circles represent Case I (Sec.~\ref{sec:numerics_case1}) simulations and orange diamonds represent Case II (Sec.~\ref{sec:numerics_case2}) simulations; empty markers are simulations with stress-free boundary conditions while filled-in markers are simulations with no-slip boundary conditions. 
We additionally conduct Case I simulations at fixed $\mR$ and $\mP$ while varying $\mS$; these simulations occur at P = 4 and R = 400 and are denoted by a green ``x.''
The two ``landmark'' simulations are denoted by boxes.
The landmark Case I simulation has $\mR = 400$ and $\mP_D = 4$.
The landmark Case II simulation has $\mR = 800$ and $\mP_L = 4$.
Both landmark simulations have $\mS = 10^3$ and no-slip boundary conditions.
\label{fig:parameter_space}
}
\end{figure}

@@

@@

\subsection{Dynamics}
In Fig.~\ref{fig:lessturb_dynamics_panels} we display snapshots of the temperature anomalies in the two ``landmark'' simulations denoted by boxes in Fig.~\ref{fig:parameter_space}.
We display the temperature anomaly in the top panel of the Case I simulation with $\mR = 400$, $\mP_D = 4$, and $\mS = 10^3$; this simulation is included in all three of our parameter space sweeps and represents the point where our ($\mR, \mP, \mS$) cuts converge  in Fig.~\ref{fig:parameter_space}.
We display the temperature anomaly in the bottom panel of the Case II simulation with $\mR = 800$, $\mP_L = 4$, and $\mS = 10^3$.
The bulk reynolds number in the convection zones of these simulations are (top) $\sim 250$ and (bottom) $\sim 350$.
Thus, these simulations are less turbulent than the simulation in Fig.~\ref{fig:vertical_dynamics_panels} (bulk Re $\sim$ 5000).
Aside from the degree of turbulence, the dynamics are very similar in Figs.~\ref{fig:vertical_dynamics_panels} \& \ref{fig:lessturb_dynamics_panels}.
In particular, we observe that hot plumes in the CZ turn into cold plumes in the PZ (as they cross the dashed horizontal lines), and hot downflows in the PZ turn into cold downflows in the CZ.
Convective plumes extend through the penetrative region and impact the stable radiative zone (above the solid horizontal line).
The convective motions excite waves at a shallow angle above the stiff radiative-convective boundary.
We note that the Case II simulation has an additional temperature inversion at the base of the simulation.
Case II simulations have a linearly increasing conductivity $k$ in the convection zone, so there is formally a small penetrative region where $\justgrad \approx \gradad > \gradrad$ at the base of the domain below the internal heating layer.

@@

\begin{figure*}[t]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
Results for Case I simulations at $\mR = 400$, $\mP = 4$, at varying $\mS$.
Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
(Left panel) Penetration heights are shown vs.~$\mS$.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{parameters_vs_re.pdf}
\caption{
(Upper left panel) Penetration heights are shown as a function of increasing Reynolds number ($\mR$) for Case I simulations (see vertical cut in Fig.~\ref{fig:parameter_space}).
We plot results both for cases with stress-free boundary conditions (SF) and no-slip boundary conditions (NS).
In both cases, we see a roughly logarithmic decrease of $\delp$ with $\mR$.
(Upper middle panel) $f$ also increases with $\mR$.
(Upper right panel) $\xi$ does not change appreciably with $\mR$ for turbulent simulations with $\mR \geq 200$.
(Lower left panel) There is a strong correlation between $\delta_{0.5}$ and $f$, agreeing with our theoretical model of Eqn.~\ref{eqn:discontinuous_prediction}.
(Lower middle panel) Changes in $f$ are roughly linearly proportional to the depth of the viscous boundary layer, $\ell_\nu$, at the bottom of the domain, at least for the open-circle SF cases.
(Lower right panel) The viscous boundary layer follows a classical scaling law seen in Rayleigh-B\'{e}nard convection, so we anticipate that $\delta_{0.5}$ and $f$ should saturate as $\mR \rightarrow \infty$ and $\ell_{\nu} \rightarrow 0$.
Boxed data points show the location of the landmark simulation from Fig.~\ref{fig:parameter_space}.
\label{fig:parameters_vs_re}
}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{mesa_profiles.pdf}
\caption{
(top) Profiles of $\justgrad$ (green), $\gradad$ (purple), and $\gradrad$ (orange) in a 1 $M_\odot$ MESA stellar model with a penetration zone.
(bottom) Sound speed differences between the model shown in the top panel and a standard (std) model run at identical parameters but without a PZ.
The addition of a PZ creates an acoustic glitch, raising the sound speed by $\mathcal{O}$(2\%) below the convection zone.
\label{fig:mesa_profiles}
}
\end{figure}

@@

In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
\begin{equation}
\int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
\label{eqn:mesa_integral_constraint}
\end{equation}
where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$, $r$ is the radial coordinate, and we write the RHS as a volume integral.
We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
\begin{equation}
\int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
\label{eqn:sphere_xi_defn}
\end{equation}
where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the PZ and CZ respectively.
Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
\begin{equation}
-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}} = (1 - f),
\label{eqn:mesa_eqn}
\end{equation}

We implemented Eqn.~\ref{eqn:mesa_eqn} in MESA (see Appendix \ref{app:mesa} for details) and evolved a $1 M_\odot$ model to an age of 4.56 Gyr with $f = 0.86$ and $\xi = 0.6$ (Eqn.~\ref{eqn:f_xi_estimates}) to qualitatively understand how our penetration parameterization modifies a stellar model.
In the top panel of Fig.~\ref{fig:mesa_profiles} we display $\justgrad \equiv d\ln T/d\ln P$ from the model which includes convective penetration.
Note that $\justgrad$ (green) remains close to $\gradad$ (purple) below the Schwarzschild convective boundary ($\gradad = \gradrad$) in a penetration zone.
After some depth $\justgrad \rightarrow \gradrad$ (orange) in the star's interior.
We additionally evolved a standard 1 $M_\odot$ MESA model to a 4.56 Gyr age without the inclusion of a PZ.
We compare the sound speed ($c$) profiles of the PZ and standard (std) model in the bottom panel of Fig.~\ref{fig:mesa_profiles}.
When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).

@@

\section{Discussion}
\label{sec:discussion}
In this work, we presented dynamical simulations of convective penetration, in which convection mixes ${\justgrad \rightarrow \gradad}$ beyond the Schwarzschild boundary.
To understand these simulations, we used an integral constraint \citep[reminiscent of][]{roxburgh1989} and flux-based arguments \citep[similar to][]{zahn1991} to derive a parameterization of convective penetration according to the convective flux and viscous dissipation.
In doing so, we have laid down the first steps (Eqns.~\ref{eqn:theory_fraction} \& \ref{eqn:mesa_eqn}) towards incorporating convective penetration into stellar structure codes.
We parameterized the viscous dissipation into a bulk-CZ portion ($f$) and a portion in the extended penetrative region ($\xi$), and derived predictions for how the height of a penetrative region, $\delp$, should scale with these measurable parameters and a new flux-based ``penetration parameter'' $\mP$.
We designed and analyzed two sets of simulations which showed good agreement with these theoretical predictions.
We briefly examined what the impliciations of this theory could be for a simple stellar model.

@@

Stellar opacities, and thus stellar radiative conductivities, are functions of thermodynamic variables rather than radial location.
The formation of a penetration zone will therefore affect the conductivity profile and $\gradrad$, which will in turn affect the location of the Schwarzschild boundary and the estimate of how deep the penetration zone should be.
In other words, convective penetration and entrainment \emph{both} occur in realistic settings, and their combined effects should be studied.
Future work should follow e.g., \citet{kapyla_etal_2017} and implement realistic opacity profiles which evolve self-consistently with the thermodynamic state in order to understand how these effects feedback into one another.

Our work here assumes a uniform composition through the convective and radiative region.
Convective boundaries often coincide with discontinuities in composition profiles \citep{salaris_cassisi_2017}.
Future work should determine if stabilizing composition gradients can prevent the formation of the penetration zones seen here.

Furthermore, stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
Dynamics in this regime may be different from those in the regime of Pr $\lesssim 1$ that we studied here, which in theory could affect $f$ and $\xi$.
Recently, \citet{kapyla2021} found that convective flows exhibited more penetration at low Pr than high Pr.
Future work should aim to understand whether $f$ and/or $\xi$ depend strongly on $\Pran$ in the turbulent regime.

@@

In summary, we have unified \citet{roxburgh1989}'s integral constraint with \citet{zahn1991}'s theory of flux-dependent penetration into a parameterized theory of convective penetration.
We tested this theory with simulations and found good agreement between the theory and our simulations.
In future work, we will use simulations to test some of the complicating factors we discussed here and aim to more robustly implement convective penetration into MESA.
